---
title: "Lab 05"
author: "Kris Seo"
date: "2/21/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = '../images/')
csv <- "https://github.com/ucb-stat133/stat133-fall-2017/raw/master/data/nba2017-players.csv"
download.file(url = csv, destfile = 'nba2017-players.csv')
dat <- read.csv('nba2017-players.csv', stringsAsFactors = FALSE)
library(dplyr)
library(ggplot2)
```

- Use slice() to subset the data by selecting the first 5 rows.
```{r}
five_rows <- slice(dat, 1:5)
```

- Use slice() to subset the data by selecting rows 10, 15, 20, ..., 50.
```{r}
five_multiples <- slice(dat , 5:50)

```

- Use slice() to subset the data by selecting the last 5 rows.
```{r}
last_five <- slice(dat , 436:441)

```

- Use filter() to subset those players with height less than 70 inches tall.
```{r}
gt_70 <- filter(dat, height < 70)
```

- Use filter() to subset rows of Golden State Warriors ('GSW').
```{r}
gsw <- filter(dat, team == 'GSW')
```

- Use filter() to subset rows of GSW centers ('C').
```{r}
c_gsw <- filter(gsw, position == 'C')
```

- Use filter() and then select(), to subset rows of lakers ('LAL'), and then display their names.
```{r}
lal <-filter(dat , team == 'LAL')
select(lal, 1)

```

- Use filter() and then select(), to display the name and salary, of GSW point guards.
```{r}
pg_gsw <- filter(gsw, position == 'PG')
select(pg_gsw,c('player','salary'))
```

- Find how to select the name, age, and team, of players with more than 10 years of experience, making 10 million dollars or less.
```{r}
exp_sal <- filter(dat, (experience > 10 & salary <= 10000000))
select(exp_sal, 'player','age', 'team')
```
- Find how to select the name, team, height, and weight, of rookie players, 20 years old, displaying only the first five occurrences (i.e. rows)
```{r}
twenty_age <- filter(dat, (age == 20))
slice(select(twenty_age, 'player','team', 'height', 'weight'), 1:5)
```


##Mutate(), Arrange()
- Using the data frame gsw, add a new variable product with the product of height and weight
```{r}
gsw <- filter(dat, team == 'GSW')
gsw <- select(gsw, player, height, weight)
gsw <- slice(gsw, c(4, 8, 10, 14, 15))
gsw
mutate(gsw, product = height * weight)

```
- Create a new data frame gsw3, by adding columns log_height and log_weight with the log transformations of height and weight.
```{r}

```
















##First contact with ggplot()
- Use the data frame gsw to make a scatterplot of height and weight.
```{r}

# scatterplot (option 1)
ggplot(data = gsw) +
  geom_point(aes(x = height, y = weight))
```
```

- Find out how to make another scatterplot of height and weight, using geom_text() to display the names of the players.
```{r}



ggplot(data = gsw, aes(x = height, y = weight, label = gsw['player'])) + geom_text()


```

- Get a scatter plot of height and weight, for ALL the warriors, displaying their names with geom_label()
````{r scatterplot3}
# scatterplot (option 3)
gsw <- filter(dat , team == 'GSW')
gsw <- select(gsw, player, height, weight)
ggplot(data = gsw, aes(x = height, y = weight, label = gsw['player'])) + geom_label()
```


- Get a density plot of salary (for all NBA players).
```{r}
ggplot(data = dat) +
  geom_density(aes(x = salary))
```

- Get a histogram of points2 with binwidth of 50 (for all NBA players).
```{r}
ggplot(data = dat) +
  geom_histogram(aex( x= points2), binwidth = 50)
```

- Get a barchart of the position frequencies (for all NBA players).
```{r}
ggplot(data = dat) +
  gemo_bar(aes(x= position))
```
- Make a scatterplot of experience and salary of all Centers, and use geom_smooth() to add a regression line.
```{r}
all_center <- filter(dat , position == 'C')
all_center <- select(all_center, player, experience, salary)
ggplot(data = all_center, aes(x = experience, y= salary))  +geom_point() + geom_smooth()
```








